Connected or Disconnected? Social Media and Social Isolationism in China

### 2023-07-06 presentations/Responsible Citizens presentation/Responsible Citizens 2023 Presentation.Rmd
Final presentation files

---
title: "Connected or Disconnected? Social Media and Social Isolationism in China"
author: "Jason Gainous and Andrew W. MacDonald"
date: "June 27th, 2023"
output: 
  learnr::tutorial:
    toc_depth: 3
bibliography: www/references.bib
nocite: '@*'
csl: www/apsa.csl
runtime: shiny_prerendered
---

@@

@@

replace_estimates <- function(mod_list) {

  for(model in 1:length(mod_list)) {
    for(obs in 1:nrow(mod_list[[model]]$tidy)) {
      mod_list[[model]]$tidy$estimate[obs] <- case_when(mod_list[[model]]$tidy$p.value[obs] > 0.05 ~ "—",
                                mod_list[[model]]$tidy$estimate[obs] >= 0 ~ "▲",
                                mod_list[[model]]$tidy$estimate[obs] < 0 ~ "▼")
    }
  }

  return(mod_list)
}

@@

```{r profileusersshortstart, context="setup"}
mod1_ord <- polr(data=china_isolation_data, human_interaction_cat ~ ses + 
                   female + CCP_member + age, Hess=TRUE)
mod2_ord <- polr(online_offline_cat ~ ses + female + CCP_member + age, 
                 data=china_isolation_data, Hess=TRUE)
mod3 <- lm(gen_social_med ~ ses + female + CCP_member + age,
           data=china_isolation_data)

@@

models <- list(
  "Human Interaction" = mod1_ord,
  "Online/Offline Interaction" = mod2_ord,
  "General Social Media" = mod3
)

# Remove the number estimates
mod_list <- modelsummary(models, output = "modelsummary_list")
mod_list <- replace_estimates(mod_list)

profile.table <- modelsummary(mod_list, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                           "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age"),
             fmt=2,
             output="gt",
             gof_map = gof.included.short,
             statistic=NULL) %>% 
  tab_footnote(footnote = n) 
```

@@

```{r socialisolationshortstart, context="setup"}
mod4 = lm(isolation ~ human_interaction + online_offline + gen_social_med + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)

mod5 = lm(isolation ~ human_interaction*urbanicity + online_offline + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)

mod6 = lm(isolation ~ online_offline*urbanicity + human_interaction + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)

mod7 = lm(isolation ~ gen_social_med*urbanicity + human_interaction + online_offline + ses + female + CCP_member + age, data = china_isolation_data)

@@

mods <- list(mod4, mod5, mod6, mod7)

# Remove the number estimates
mod_list <- modelsummary(mods, output = "modelsummary_list")
mod_list <- replace_estimates(mod_list)

socisotable <- modelsummary(mod_list, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age",
                             "urbanicity" = "Urbanicity",
                             "online_offline" = "Online-Offline",
                             "human_interaction" = "Human Interaction",
                             "gen_social_med" = "Social Media",
                             "human_interaction:urbanicity" = 
                               "Human Interaction*Urbanicity",
                             "online_offline:urbanicity" =
                               "Online-Offline*Urbanicity",
                             "gen_social_med:urbanicity" = 
                               "Social Media*Urbanicity"),
             fmt=2,
             output="gt",
             gof_map = gof.included.short,
             statistic = NULL) %>% 
  tab_footnote(footnote = n) %>% 
  tab_header("Response variable: social isolation")
```

@@

```{r marginsetup, context="server-start"}
  mod5 = lm(isolation ~ human_interaction*urbanicity + online_offline 
            + gen_social_med + ses + female + CCP_member + age, 
            data = china_isolation_data)

  mod6 = lm(isolation ~ online_offline*urbanicity + human_interaction 
            + gen_social_med + ses + female + CCP_member + age, 
            data = china_isolation_data)

  mod7 = lm(isolation ~ gen_social_med*urbanicity + human_interaction 
            + online_offline + ses + female + CCP_member + age, 
            data = china_isolation_data)

  a <- plot_model(mod5, type = "pred", title = "",
                  terms = c("human_interaction", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) +
    ylab("") +
    xlab("Digital Human Interaction") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))

  b <- plot_model(mod6, type = "pred", title = "", 
                  terms = c("online_offline", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) +
    ylab("") +
    xlab("Online to Offline Relationships") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))

  c <- plot_model(mod7, type = "pred", title = "", 
                  terms = c("gen_social_med", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) + 
    ylab("") +
    xlab("Social Media Use") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))  
```

@@

modelsfull <- list(
  "Human Interaction" = mod1_ordfull,
  "Online/Offline Interaction" = mod2_ordfull,
  "General Social Media" = mod3full
)

@@

modelsummary(modelsfull, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age"),
             fmt=2,
             stars=c("*" = 0.05),
             output="kableExtra",
             gof_map = gof.included.full) %>% 
  footnote(general = n, threeparttable = TRUE)
```

@@

modsfull <- list(mod4full, mod5full, mod6full, mod7full)

modelsummary(modsfull, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age",
                             "urbanicity" = "Urbanicity",
                             "online_offline" = "Online-Offline",
                             "human_interaction" = "Human Interaction",
                             "gen_social_med" = "Social Media",
                             "human_interaction:urbanicity" = 
                               "Human Interaction*Urbanicity",
                             "online_offline:urbanicity" =
                               "Online-Offline*Urbanicity",
                             "gen_social_med:urbanicity" = 
                               "Social Media*Urbanicity"),
             fmt=2,
             stars=c("*" = 0.05),
             output="kableExtra",
             gof_map = gof.included.full) %>% 
  footnote(general = n, threeparttable = TRUE)
```

>>>>

---
title: "Connected or Disconnected? Social Media and Social Isolationism in China"
author: "Jason Gainous and Andrew W. MacDonald"
date: "June 27th, 2023"
output: 
  learnr::tutorial:
    toc_depth: 2
bibliography: www/references.bib
nocite: '@*'
csl: www/apsa.csl
runtime: shiny_prerendered
---

@@

replace_estimates <- function(mod_list_func) {

  working <- mod_list_func

  for(model in 1:length(working)) {
    for(obs in 1:nrow(working[[model]]$tidy)) {
      working[[model]]$tidy$estimate[obs] <- case_when(working[[model]]$tidy$p.value[obs] > 0.05 ~ "—",
                                working[[model]]$tidy$estimate[obs] >= 0 ~ "▲",
                                working[[model]]$tidy$estimate[obs] < 0 ~ "▼")
    }
  }

  return(working)
}

@@

@@

```{r profileusersshortstart, context="data"}
mod1_ord_short <- polr(data=china_isolation_data, human_interaction_cat ~ ses + 
                   female + CCP_member + age, Hess=TRUE)
mod2_ord_short <- polr(online_offline_cat ~ ses + female + CCP_member + age, 
                 data=china_isolation_data, Hess=TRUE)
mod3_short <- lm(gen_social_med ~ ses + female + CCP_member + age,
           data=china_isolation_data)

@@

mods_prof <- list(
  "Human Interaction" = mod1_ord_short,
  "Online/Offline Interaction" = mod2_ord_short,
  "General Social Media" = mod3_short
)

# Remove the number estimates
mod_list_prof <- modelsummary(mods_prof, output = "modelsummary_list")
mod_list_prof_update <- as.list(mod_list_prof)
mod_list_prof_update <- replace_estimates(mod_list_prof_update)

profile.table <- modelsummary(mod_list_prof_update, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                           "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age"),
             fmt=2,
             output="gt",
             gof_map = gof.included.short,
             statistic=NULL) %>% 
  tab_footnote(footnote = n) 
```

@@

```{r socialisolationshortstart, context="data"}
mod4short = lm(isolation ~ human_interaction + online_offline + gen_social_med + urbanicity + ses + female + CCP_member + age, data = china_isolation_data)

mod5short = lm(isolation ~ human_interaction*urbanicity + online_offline + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)

mod6short = lm(isolation ~ online_offline*urbanicity + human_interaction + gen_social_med + ses + female + CCP_member + age, data = china_isolation_data)

mod7short = lm(isolation ~ gen_social_med*urbanicity + human_interaction + online_offline + ses + female + CCP_member + age, data = china_isolation_data)

@@

mods_soc <- list(mod4short, mod5short, mod6short, mod7short)

# Remove the number estimates
mod_list_soc <- modelsummary(mods_soc, output = "modelsummary_list")
mod_list_soc_update <- as.list(mod_list_soc)
mod_list_soc_update <- replace_estimates(mod_list_soc_update)

socisotable <- modelsummary(mod_list_soc_update, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age",
                             "urbanicity" = "Urbanicity",
                             "online_offline" = "Online-Offline",
                             "human_interaction" = "Human Interaction",
                             "gen_social_med" = "Social Media",
                             "human_interaction:urbanicity" = 
                               "Human Interaction*Urbanicity",
                             "online_offline:urbanicity" =
                               "Online-Offline*Urbanicity",
                             "gen_social_med:urbanicity" = 
                               "Social Media*Urbanicity"),
             fmt=2,
             output="gt",
             gof_map = gof.included.short,
             statistic = NULL) %>% 
  tab_footnote(footnote = n) %>% 
  tab_header("Response variable: social isolation")
```

@@

```{r marginsetup, context="server-start"}
  mod5margin = lm(isolation ~ human_interaction*urbanicity + online_offline 
            + gen_social_med + ses + female + CCP_member + age, 
            data = china_isolation_data)

  mod6margin = lm(isolation ~ online_offline*urbanicity + human_interaction 
            + gen_social_med + ses + female + CCP_member + age, 
            data = china_isolation_data)

  mod7margin = lm(isolation ~ gen_social_med*urbanicity + human_interaction 
            + online_offline + ses + female + CCP_member + age, 
            data = china_isolation_data)

  a <- plot_model(mod5margin, type = "pred", title = "",
                  terms = c("human_interaction", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) +
    ylab("") +
    xlab("Digital Human Interaction") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))

  b <- plot_model(mod6margin, type = "pred", title = "", 
                  terms = c("online_offline", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) +
    ylab("") +
    xlab("Online to Offline Relationships") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))

  c <- plot_model(mod7margin, type = "pred", title = "", 
                  terms = c("gen_social_med", "urbanicity"), 
                  legend.title = "Urbanicity") +
    scale_color_discrete(labels = c("Village", "Small City", 
                                    "Mid-sized City", "Suburb", "Big City")) + 
    ylab("") +
    xlab("Social Media Use") +
    theme(panel.border = element_rect(color = "black",fill = NA, size = 1))  
```

@@

modelsfull_prof <- list(
  "Human Interaction" = mod1_ordfull,
  "Online/Offline Interaction" = mod2_ordfull,
  "General Social Media" = mod3full
)

@@

modelsummary(modelsfull_prof, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age"),
             fmt=2,
             stars=c("*" = 0.05),
             output="kableExtra",
             gof_map = gof.included.full) %>% 
  footnote(general = n, threeparttable = TRUE)
```

@@

modsfull_soc <- list(mod4full, mod5full, mod6full, mod7full)

modelsummary(modsfull_soc, 
             coef_omit = ".*Connect|.*Intercept|.*No|.*Yes",
             coef_rename = c("ses" = "SES",
                             "female" = "Female",
                             "CCP_member" = "CCP Member",
                             "age" = "Age",
                             "urbanicity" = "Urbanicity",
                             "online_offline" = "Online-Offline",
                             "human_interaction" = "Human Interaction",
                             "gen_social_med" = "Social Media",
                             "human_interaction:urbanicity" = 
                               "Human Interaction*Urbanicity",
                             "online_offline:urbanicity" =
                               "Online-Offline*Urbanicity",
                             "gen_social_med:urbanicity" = 
                               "Social Media*Urbanicity"),
             fmt=2,
             stars=c("*" = 0.05),
             output="kableExtra",
             gof_map = gof.included.full) %>% 
  footnote(general = n, threeparttable = TRUE)
```
